### 2020-04-23 writeup/setup.tex
setup

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
	In particular, if model shift is too large, we get negative transfer from multi-task training. [\textbf{done}]
	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
	\item {\bf Covariate shift affects the rate of transfer:} next we show that if we optimize the multi-task model on the target task, this can correct the negative transfer.
	We further show that covariate shift controls the rate in which transfer occurs. [\textbf{1/2 done}]
\end{enumerate}

Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
\todo{We show the following results.} [\textbf{1/2 done}]

>>>>

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.
Our main results are described as follows.
\begin{enumerate}
	\item {\bf De-noising effect of information transfer.}
	We provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
	\item {\bf Effects of covariate shift, model distance, and data ratio.}
	We apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
	\begin{enumerate}
		\item {\bf Multi-task training over single-task training.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
	In particular, if model shift is too large, we get negative transfer from multi-task training.
		\item {\bf Transfer learning over single-task training.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
		\item {\bf Transfer learning over multi-task training.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
		The amount of improvement becomes more significant as the model distance becomes larger.
	\end{enumerate}
	\item {\bf Extending to many tasks with the same covariates.} For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
	We show that our results and insights from the above can be extended to this setting as well.
\end{enumerate}
